\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-28 manuscript/main.tex
modified:   analysis/quantile-regression.R 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_estimate.ipynb 	modified:   network_estimation/network_estimation.ipynb 	new file:   network_estimation/network_structure.ipynb

@@

>>>>

We decided to use the so called Change-in-Change (CIC) estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the

@@

  \bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
  Athey, S., and G. W. Imbens. 2006. Identification and Inference in Nonlinear Difference-in-Differences Models. \textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.
